---
title: "Report MOVID-IMPACT survey"
subtitle: 'Stay home, stay safe: Why are people in Chile not complying with stay-at-home recommendations and restrictions?<br>ANID-COVID N°960 “CoV-IMPACT-C”'
author: "by Valentina Andrade"
lang: es-CL
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: yes
    depth: 2
    theme: cerulean
    number_sections: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, results = 'asis')
summarytools::st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives better results.
#summarytools::st_css()

library(ggplot2); theme_set(theme_classic() + theme(text = element_text(size = 12)))
library(knitr);  options(knitr.kable.NA = 'No sabe/No responde')
kable <- function(data) {
  knitr::kable(data, booktabs = T, digits = 3) %>% kable_styling(latex_options =c("striped", "scale_down"),bootstrap_options = c("striped", "hover", "responsive", "condensed"))
}
```

```{r packages, echo = F}
# 1. Cargar paquetes
pacman::p_load(tidyverse, kableExtra, sjPlot)
# 2. Cargar tablas
movid_i <- readRDS("../../output/data/movid_impact_proc.RDS")
```
----

```{r recode}
data <- movid_i %>% ungroup() %>%  
  mutate(across(c(starts_with("comp")), ## Compliance
                ~case_when(
                  . == "Always" ~ 1,
                  is.na(.) ~ NA_real_,
                  TRUE ~ 0)), 
         across(c(per_risk), ~as.numeric(.)), ## Instrumental A 
          leg_enforce = case_when( ## Instrumental B
           leg_enforce %in% c("Strongly disagree", "Disagree") ~ 1,
           is.na(leg_enforce) ~ NA_real_,
           TRUE ~ 0),
         leg_enforce = factor(leg_enforce),
         normas = (as.numeric(normas)*-1)+7, ## Normative A
         norms = if_else(nocumple_normas == 1,0,1), #Creo
         soc2_obedecer = (as.numeric(soc2_obedecer)*-1)+7) ##Normative B
```


# Descriptive

## Compliance

In the last week, how often have you done the following actions to protect yourself from coronavirus?

### Wash your hands for 20 seconds

```{r wash}
data %>% group_by(comp_wash) %>% 
    summarise( n = n(),
      percent = 100 * n() / nrow(movid_i)) %>%
  kable()
```

### Keep at least two meters away from people around you.

```{r distance}
data %>% group_by(comp_dist) %>% 
    summarise( n = n(),
      percent = 100 * n() / nrow(movid_i)) %>%
  kable()
```

### Avoid meeting with more than 10 persons in an closed place.
  
```{r social}
data %>% group_by(comp_soc) %>% 
    summarise( n = n(),
      percent = 100 * n() / nrow(movid_i)) %>%
  kable()
```

### Wear a mask when you leave home

```{r mask home}
data %>% group_by(comp_mask) %>% 
    summarise( n = n(),
      percent = 100 * n() / nrow(movid_i)) %>%
  kable()
```

### Wear a mask when you meet other people in an closed place.

```{r mask places}
data %>% group_by(comp_mask2) %>% 
    summarise( n = n(),
      percent = 100 * n() / nrow(movid_i)) %>%
  kable()
```


## Sociodemographic

### Sex

```{r sex}
data %>% group_by(sex) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```

### Age

```{r age}
data %>% ungroup() %>% 
summarytools::descr(., var = age, stats = "common")
```

```{r age2}
data %>% group_by(age_3cat) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```

### Education

```{r educ}
data %>% group_by(educ_3cat) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```

### Occupation

```{r occup}
data %>% group_by(work) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```


### Household income (log)

```{r income}
summarytools::descr(data, var = income_hh, stats = "common")
```


### Health risk

```{r healthrisk}
data %>% group_by(cronicos) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```

### Health insurance

```{r healthinsurance}
data %>% group_by(prev_4categ) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```

### Lockdown

```{r lockdown}
data %>% group_by(lockdown) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
```


## Instrumental factors

### A. Perived risk

How dangerous do you think Coronavirus is for you and your closest one?

```{r per_risk}
data %>% group_by(per_risk) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(high_risk) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(low_risk) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()

```

### B. Legal enforcement

In Chile, if any person goes out without permission during a lockdown, it is very unlikely that this person will be inspected and punished.

```{r leg-inf}
data %>% group_by(leg_enforce) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(high_leg) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(low_leg) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()

```


## Normative factors

### A. Perceived social norms

Thinking about the different coronavirus care measures ( staying at home, wearing a mask, keeping a social distance or washing your hands), to what extent would you say that your closest ones (people who live with you or your close family) comply with these recommendations?

```{r normas}
data %>% group_by(normas) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(cumple_normas) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(nocumple_normas) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()
data %>% group_by(norms) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()


```

### B. Legitimacy

Even if we sometimes disagree with the health authorities and the measures they propose, it is our duty to accuratly follow their indications.

```{r obedecer}
data %>% group_by(soc2_obedecer) %>% 
    summarise(n = n(), percent = 100 * n() / nrow(data)) %>% kable()

```


Now, we evaluated the correlation of the item `soc2_obey` with two more items of the same battery: 

- `soc1_welfare`: Government authorities have prioritized the welfare of the population over other political and economic interests.

- `soc3_gob`: Although we sometimes disagree with health authorities and the measures they propose, it is our duty to accuratly follow their indications.


```{r corr}
aux <- data %>% select(starts_with("soc")) %>% mutate_at(vars(1:3),funs(as.numeric(.))) 


```

As we can see, the item of interest `soc2_obey` has a very low correlation with the rest of the items, while among them there is a medium correlation. Consequently, only the item that was initially defined to measure legitimacy (*soc2_obey*) should be chosen. 

# Models {-}

```{r model-estimate, eval = T}

predictors <- c("sex + age + educ_3cat +  cronicos + 
                  prev_4categ + work + lockdown +  
                  per_risk + leg_enforce +
                  cumple_normas + soc2_obedecer")

#saque income_hh

m_wash  <- glm(as.formula(paste0("comp_wash ~", predictors)), 
                data=data, family="binomial")
m_dist   <- glm(as.formula(paste0("comp_dist ~", predictors)),
                data=data, family="binomial")
m_soc <- glm(as.formula(paste0("comp_soc ~", predictors)),
                data=data, family="binomial")
m_mask   <- glm(as.formula(paste0("comp_mask ~", predictors)),
                data=data, family="binomial")
m_mask2  <- glm(as.formula(paste0("comp_mask2 ~", predictors)),
                data=data, family="binomial")

```

```{r model-tab, eval = T}
tab_model(m_wash, m_dist, m_soc, m_mask, m_mask2)
```
